\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-11-02 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Minor changes

However, recently reported CCSN simulations using two-moment neutrino transport with algebraic closures have employed Eddington factors that can violate the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
As examples, we consider the Eddington factors discussed in \cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} may work fine when the occupancy is low.  
When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
The Eddington factor of Janka~1~\cite{janka_1991} may violate both the upper and lower bound on the Eddington factor.  
Only the closure due to Cernohorsky~\&~Bludman~\cite{cernohorskyBludman_1994} satisfies both the upper and lower bounds.  
This is not suprising as this is the only closure based on Fermi-Dirac statistics.  
Althought the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.  
When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.  
\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.

>>>>

However, recently reported CCSN simulations using two-moment neutrino transport with algebraic closures have employed Eddington factors that can violate the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}.  
As examples, we consider the Eddington factors discussed in \cite{murchikova_etal_2017}, where the suitability of several algebraic closures for two-moment neutrino transport was evaluated.  
In Fig.~\ref{fig:EddingtonFactorsWithDifferentClosure}, we plot the Eddington factor versus the flux factor for two occupancies; $\cJ = 0.1$ (low occupancy) and $\cJ = 0.9$ (high occupancy).  
Of the algebraic closures plotted, few satisfy the bounds on the Eddington factor in Eq.~\eqref{eq:eddingtonFactorBounds}.  
Kershaw~\cite{kershaw_1976}, Wilson~\cite{wilson_1975,leblancWilson_1970}, Levermore~\cite{levermore_1984}, Minerbo~\cite{minerbo_1978}, and Janka~2~\cite{janka_1992} may work fine when the occupancy is low.  
When the occupancy is high, the Eddington factor due to these closures exceeds the upper bound for Fermi-Dirac statistics.  
The Eddington factor of Janka~1~\cite{janka_1991} may violate both the upper and lower bound on the Eddington factor.  
Only the closure due to Cernohorsky~\&~Bludman~\cite{cernohorskyBludman_1994} satisfies both the upper and lower bounds.  
This is not surprising as this is the only closure based on Fermi-Dirac statistics.  
Although the Levermore and Minerbo closures do not satisfy the bounds in Eq.~\eqref{eq:eddingtonFactorBounds}, they are widely used in simulations of neutrino transport in CCSNe \ee{and neutron star mergers?}; e.g., O'Connor \& Couch~\cite{oConnorCouch_2018}, Pan et al.~\cite{pan_etal_2018}, Glas et al.~\cite{glas_etal_2018}, and Just et al.~\cite{just_etal_2018} use the Minerbo closure, while Vartanyan et al.~\cite{vartanyan_etal_2018}, Cabezon et al.~\cite{cabezon_etal_2018}, and Kuroda et al.~\cite{kuroda_etal_2016} use the Levermore closure.  
When employing these closures in conditions of high occupancy, a numerical scheme may evolve the moments outside the realizable domain of Fermi-Dirac statistics given in Eq.~\eqref{eq:MomentsBounds}.  
\ee{so what?  Should we discuss the presence of blocking factors in collision terms?}
%With those algebraic closures that don't conserve the bounds, the time integrator may give moments that implies $f>1$.
%Some safety protections may be applied for those method, but the safety protections can break the conservation laws in lepton number or energy and defect the CCSN simulation.
